The effects of varying depth in cosmic shear surveys

### 2019-10-02 paperdraft.tex
minor changes
added link to paper in abstract

\documentclass{aa}

@@

\usepackage{bm}
\usepackage{verbatim}
%
\usepackage{graphicx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
\usepackage{subcaption}

@@

   \author{Sven Heydenreich\inst{1}%\fnmsep\thanks{sven@astro.uni-bonn.de}
          \and Peter Schneider\inst{1} 
          \and Hendrik Hildebrandt\inst{2,1}
          \and Catherine Heymans\inst{3,2} 
          \and Marika Asgari\inst{3}
          \and Jan Luca van den Busch\inst{2,1}
          \and Chieh-An Lin\inst{3}
          \and Benjamin Joachimi\inst{4}
          \and Tilman Tr\"{o}ster\inst{3}
          }
   \institute{Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn, Germany 
\and 
Astronomisches Institut, Ruhr-Universit\"at Bochum, Universit\"atsstr. 150, 44801 Bochum, Germany 
\and
Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK
\and
Department of Physics and Astronomy, University College London, Gower Street, London WC1E 6BT, UK
% \and
% Service d'Astrophysique, CEA Saclay, Orme des Merisiers, B\^at 709, 91191 Gif-sur-Yvette, France
% \and 
% Fenglin Veteran Hospital, 2 Zhongzheng Rd. Sec. 1, Fenglin Township, Hualien 97544, Taiwan
\\ \email{sven@astro.uni-bonn.de, peter@astro.uni-bonn.de}
             }

@@

  \abstract
% context (optional)
   {Cosmic shear proves to be a powerful tool to study the properties of the Universe. The discrepancy in the parameter $S_8 = \sigma_8\sqrt{\Omega_{\rm{m}}/0.3}$ between measurements in the local Universe and the cosmic microwave background motivates further investigation of yet unaccounted systematic biases. 
% aims
   Ground-based surveys are subject to a variation in depth caused by varying atmospheric conditions; we investigate and quantify the resulting effects. In particular, we check whether they introduce a bias to the resulting cosmological parameters and if they can be responsible for the occurrence of B-modes.
% methods
   We construct a semi-analytic model to estimate the impact on the shear correlation functions and analyse the implications for cosmological parameters. Furthermore, we construct COSEBIs from the correlation functions to quantify the occurring B-modes.
% results
   For the Kilo-Degree Survey this effect introduces an error in $\xi_\pm$ of the order of a few percent on small scales. We find that the resulting bias in $\Omega_{\rm m}$, $\sigma_8$ and $S_8$ will be significant in next-generation cosmic shear surveys. We find that the dependence of this effect on the underlying cosmology is not negligible. We also report the occurrence of B-modes, although at a not yet significant level.
% conclusions (optional)
   We conclude that the effects of varying depth for current cosmic shear surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments.}

>>>>

\documentclass{aa}  
\usepackage{hyperref}

@@

\usepackage{bm}
\usepackage{verbatim}
%
\usepackage{graphicx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
\usepackage{subcaption}
%\usepackage{hyperref}

@@

   \author{Sven Heydenreich\inst{1}%\fnmsep\thanks{sven@astro.uni-bonn.de}
          \and Peter Schneider\inst{1} 
          \and Hendrik Hildebrandt\inst{2,1}
          \and Marika Asgari\inst{3}
          \and Catherine Heymans\inst{3,2} 
          \and Benjamin Joachimi\inst{4}
          \and Chieh-An Lin\inst{3}
          \and Tilman Tr\"{o}ster\inst{3}
          \and Jan Luca van den Busch\inst{2,1}
          }
   \institute{Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn, Germany 
\and 
Astronomisches Institut, Ruhr-Universit\"at Bochum, Universit\"atsstr. 150, 44801 Bochum, Germany 
\and
Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK
\and
Department of Physics and Astronomy, University College London, Gower Street, London WC1E 6BT, UK
% \and
% Service d'Astrophysique, CEA Saclay, Orme des Merisiers, B\^at 709, 91191 Gif-sur-Yvette, France
% \and 
% Fenglin Veteran Hospital, 2 Zhongzheng Rd. Sec. 1, Fenglin Township, Hualien 97544, Taiwan
\\ \email{sven@astro.uni-bonn.de, peter@astro.uni-bonn.de}
             }

@@

  \abstract
   {Cosmic shear proves to be a powerful tool to study the properties of the Universe. The discrepancy in the parameter $S_8 = \sigma_8\sqrt{\Omega_{\rm{m}}/0.3}$ between measurements in the local Universe and the cosmic microwave background motivates further investigation of yet unaccounted systematic biases. 
   Ground-based surveys are subject to a variation in depth caused by varying atmospheric conditions; we investigate and quantify the resulting effects. In particular, we check whether they introduce a bias to the resulting cosmological parameters and if they can be responsible for the occurrence of B-modes.
   We construct a semi-analytic model to estimate the impact on the shear correlation functions and analyse the implications for cosmological parameters. Furthermore, we construct COSEBIs from the correlation functions to quantify the occurring B-modes.
   For the Kilo-Degree Survey this effect introduces an error in $\xi_\pm$ of the order of a few percent on small scales. We find that the resulting bias in $\Omega_{\rm m}$, $\sigma_8$ and $S_8$ will be significant in next-generation cosmic shear surveys. We find that the dependence of this effect on the underlying cosmology is not negligible. We also report the occurrence of B-modes, although at a not yet significant level.
   We conclude that the effects of varying depth for current cosmic shear surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments. \textcolor{blue}{\href{https://docs.google.com/document/d/13j7fUE8jrK5HOVbf4p0HdQs6c14jbWtm9Yq8CtLZCK4/edit?usp=sharing}{[Link to the current google doc]}}}
